
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% University/School Laboratory Report
% LaTeX Template
% Version 3.1 (25/3/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Linux and Unix Users Group at Virginia Tech Wiki 
% (https://vtluug.org/wiki/Example_LaTeX_chem_lab_report)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}
\usepackage[margin=1.3in]{geometry}
\usepackage{hyperref}
\usepackage[version=3]{mhchem} % Package for chemical equation typesetting
\usepackage{siunitx} % Provides the \SI{}{} and \si{} command for typesetting SI units
\usepackage{graphicx} % Required for the inclusion of images
\usepackage{natbib} % Required to change bibliography style to APA
\usepackage{amsmath} % Required for some math elements 

\setlength\parindent{1em} % Removes all indentation from paragraphs
\setlength{\parskip}{1em}
\renewcommand{\labelenumi}{\alph{enumi}.} % Make numbering in the enumerate environment by letter rather than number (e.g. section 6)

%\usepackage{times} % Uncomment to use the Times New Roman font

%----------------------------------------------------------------------------------------
%	DOCUMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{Weekly Catchup} % Title

\author{Weixiong Zheng} % Author name

\date{March 08, \today} % Date for the report

\begin{document}

\maketitle % Insert the title, author and date
% If you wish to include an abstract, uncomment the lines below
% \begin{abstract}
% Abstract text
% \end{abstract}

%----------------------------------------------------------------------------------------
%	SECTION 0
%----------------------------------------------------------------------------------------
\section{Updates on previous goals}
\begin{itemize}
	\item Transferring CTest to GTest to the maximum extent
	\item Small meetings for task planning and progress checking
\end{itemize}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Progress up to now}
\subsection{Marissa}
A bunch of small meetings were scheduled with Marissa to help debug her code. I am comfortable
with the current way Marissa working with me. The only thing is the debugging process 
took a lot of cautions and patience to find out not only coding bugs but also mathematical
errors. It's slow but progressing gradually.

One of the meetings with Marissa involved things which has to be done. A diagram was created 
thereafter to better aid tracking her progress. It should be reasonable for August-deadline time line.

\subsection{BART}
The past few weeks were coding/PR heavy weeks. It included transferring unit tests from CTest to GTest, Redesigning/formatting codes, reviewing/committing to PR and investigating cell-number related error \url{https://github.com/SlaybaughLab/BART/issues/9}.

Most part is going smoothly except for the error investigation. I will revisit the investigation until everything else for the restart is ready.

Josh are starting well and we are collaborating super fine in terms of idea discussing, detailing implementation and PR reviewing.

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------
\section{Things you need from Rachel}
As the first contract ends on \today, I may need Rachel to contact HR person to see what 
has to be done for the extension.

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------
\section{Goals/Things will be going on}
The process of restart involves a lot of thought and helpful discussions between me and Josh.
It gives a good idea about how and what to do with {\tt BARTDriver} and how we treat free functions and global variables. This will be the first main goals until the next check-in. Also, some dense meetings will be held before April, when Josh's baby comes into this new world. He'd like to get as much done as possible so I will be at his assistance.

The other thing is to help Marissa get the code running. It might just be as time consuming as it used to be usually.

%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------
\section{Links to any related materials}
A shared folder has been created and access invitations have been sent to Rachel, Marissa and 
Josh. Here are the links for public access:
\begin{itemize}
	\item BART: \url{https://www.dropbox.com/sh/5p340f5bs7k6wt3/AACbdvExIjzhLG4l4aqGgV-Ta?dl=0}
	\item Marissa: \url{https://www.dropbox.com/sh/hslgnvovvxigs6j/AABpcwP6bfquVoP-AIp5wwRra?dl=0}
	\item Josh: \url{https://www.dropbox.com/sh/el2b303k9avjqvd/AABiMkuBiZOcThUg1bhvYUSoa?dl=0}
\end{itemize}


%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

%\bibliographystyle{apalike}
%
%\bibliography{sample}

%----------------------------------------------------------------------------------------


\end{document}